On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-03 tt_theorem.tex
before lunch 12/3

\begin{theorem}[Tunnel Troll Theorem]
Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$. 
At arity $\alpha \geq 3$, if $S[k] = t$ and $S[k+1] \neq \blacksquare$, then $\#bc(C_{k-1}) > \#bc(C_k)$.
On the other hand, at arity $\alpha = 2$, if there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
\end{theorem}

>>>>

\begin{theorem}[Tunnel Troll Theorem]
Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$. The following statements hold.
\begin{enumerate}
\item At arity $\alpha \geq 3$, if $S[k] = t$ (i.e. the tunnel that stabilizes $w[k]$ is not singular) and $S[k+1] \neq \blacksquare$, then $\#bc(C_{k-1}) > \#bc(C_k)$.
\item At arity $\alpha = 2$, if there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
\end{enumerate}
\end{theorem}
